### 2019-03-24 Sections/the_quantum_mind.tex
minor

\comment{Tidying, editing, proofing, structure.}

\comment{Introductory lead in. To do.}

\subsection{Introduction}

@@

This is not yet an active research area in its own right. However, there are some preliminary toolkits that are starting to be developed in the new field of quantum machine learning (QML). By first summarising the intersection between the classical internet and classical machine learning, we gain insight into the kinds of tools required to start examining their quantum counterparts. For instance, we will see how aspects of quantum processing of quantum data might be aided by machine learning, how machine learning may be enhanced by quantum resources, and how machine learning may be implemented in these distributed quantum settings. A summary is presented in Tab.~\ref{tab:CommTable2}.

@@

To find algorithms practically viable in the the near future, research is increasingly devoting its attention to hybrid classical-quantum algorithms. These algorithms, which include variational methods for optimisation \cite{bib:moll2018quantum}, exhibit low circuit-depth, where the optimisation process is performed iteratively and classically. There are roughly two varities: one that attempts to enhance classical algorithms with classical input data; and another where the quantum advantage lies in efficient quantum state preparation, thus relying on quantum input data. Prominent examples of the former include quantum approximate optimisation algorithms\index{Quantum approximate optimisation algorithms} (QAOA) \cite{bib:farhi2014quantum, bib:farhi2016quantum}, and the latter includes variational quantum eigensolvers (VQE) \cite{bib:peruzzo2014peruzzo, bib:kandala2017hardware}, which we return to in the subsequent section.

>>>>

\comment{Tidying, editing, proofing, structure. Section titles.}\\

\dropcap{I}{n} recent years, the implementation of artificial intelligence via machine learning techniques has become a forefront area of research, transforming many software industries and those that depend upon them. An obvious question to ask is to what extent machine learning techniques translate across to the quantum computing environment, and whether upon doing so there is an associated quantum enhancement. While this field of \textit{quantum machine learning} (QML) is far too extensive to summarise here, we will instead present a brief overview of how machine learning might apply in a networked quantum environment.

There are two distinct avenues to consider here. First, how does machine learning influence the operation of quantum networks? Second, how do quantum networks affect the implementation of machine learning? We will outline some of the key considerations here from both these opposing angles of consideration.

\subsection{Overview}

@@

This is not yet an active research area in its own right. However, there are some preliminary toolkits that are starting to be developed in the new field of QML. By first summarising the intersection between the classical internet and classical machine learning, we gain insight into the kinds of tools required to start examining their quantum counterparts. For instance, we will see how aspects of quantum processing of quantum data might be aided by machine learning, how machine learning may be enhanced by quantum resources, and how machine learning may be implemented in these distributed quantum settings. A summary is presented in Tab.~\ref{tab:CommTable2}.

@@

To find algorithms practically viable in the the near future, research is increasingly devoting its attention to hybrid classical-quantum algorithms. These algorithms, which include variational methods for optimisation \cite{bib:moll2018quantum}, exhibit low circuit-depth, where the optimisation process is performed iteratively and classically. There are roughly two varieties: one that attempts to enhance classical algorithms with classical input data; and another where the quantum advantage lies in efficient quantum state preparation, thus relying on quantum input data. Prominent examples of the former include quantum approximate optimisation algorithms\index{Quantum approximate optimisation algorithms} (QAOA) \cite{bib:farhi2014quantum, bib:farhi2016quantum}, and the latter includes variational quantum eigensolvers (VQE) \cite{bib:peruzzo2014peruzzo, bib:kandala2017hardware}, which we return to in the subsequent section.
